\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Tweak wording

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace. The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data. Thus, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

@@

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are enforeced with transparency. The appearance of smart contracts meet different requirements of trading pattern.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games consists of several repetitions of the same base game which meets the scenario of data subscription.

>>>>

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization, blockchain
\end{IEEEkeywords}

@@

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amounts of data emerges, people have started to explore the design of data marketplaces. The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data. Thus, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a DLT-based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

@@

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. All conditions and states established in the contract are enforeced with transparency. The appearance of smart contracts meet different requirements of trading pattern.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games fits the scenario of data subscription.
